Exploring how changes in age at death and cause of death have narrowed the black-white life expectancy gap over forty-five years in the United States.

### 2017-01-04 Manuscript/Manuscript.Rmd
add state abbrevs

```{r figure5, fig.align="center", fig.height=8, fig.width=8, echo=F}
ggplotly(ggplot(subset(BlackWhite, Sex2 == "Male"), aes(y=WBgap.s, x = Year3)) + geom_line(aes(col = State2))
         + facet_wrap(~Census_Region) +
           ylab("Black-white life expectancy gap (years)") +
           xlab("Year") #+
           #geom_text(data = subset(BlackWhite, Year3 == 2010), aes(label = State2), check_overlap = T)
         )
```

@@

```{r figure6, fig.align="center", fig.height=8, fig.width=8, echo=F}
ggplotly(ggplot(subset(BlackWhite, Sex2 == "Female"), aes(y=WBgap.s, x = Year3)) + geom_line(aes(col = State2))
         + facet_wrap(~Census_Region))
```

>>>>

```{r figure5, fig.align="center", fig.height=8, fig.width=8, echo=F}
ggplotly(ggplot(subset(BlackWhite, Sex2 == "Male"), aes(y=WBgap.s, x = Year3)) + geom_line(aes(col = State2))
         + facet_wrap(~Census_Region) +
           ylab("Black-white life expectancy gap (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite, Year3 == 2013 & Sex2 == "Male"), aes(label = stabbrs), check_overlap = T) #+
           #scale_x_continuous(limits = c(1969, 2020))
         ) 
```

@@

```{r figure6, fig.align="center", fig.height=8, fig.width=8, echo=F}
ggplotly(ggplot(subset(BlackWhite, Sex2 == "Female"), aes(y=WBgap.s, x = Year3)) + geom_line(aes(col = State2))
         + facet_wrap(~Census_Region) +
           ylab("Black-white life expectancy gap (years)") +
           xlab("Year") +
           geom_text(data = subset(BlackWhite, Year3 == 2013 & Sex2 == "Female"), aes(label = stabbrs), check_overlap = T))
```
